Large Linear Multi-output Gaussian Process Learning for Time Series

### 2017-05-08 paper/paper.tex
nips paper future work corrections, rm comment

LLGP performed slightly worse than COGP in SMSE, but both NLPD and runtime indicate significant improvements (Tbl.~\ref{weather-tbl}). Varying the number of interpolating points $m$ from $500$ to $1000$ constructs a tradeoff frontier between increases in $m$ and NLPD decrease at the cost of additional runtime (Fig.~\ref{fig:llgpweather}). While NLPD improvement diminishes as $m$ increases, LLGP is still an improvement compared to COGP for a range of $m$ by an order of magnitude in runtime and almost two orders of magnitude for NLPD.

@@

LLGP provides a means to approximate the log-likelihood function gradients through interpolation. We have shown on several datasets that this can be done in a way that is faster and leads to more accurate results than variational approximations.

@@

% \begin{table}[t]
%   \caption{Sample table title}
%   \label{sample-table}
%   \centering
%   \begin{tabular}{lll}
%     \toprule
%     \multicolumn{2}{c}{Part}                   \\
%     \cmidrule{1-2}
%     Name     & Description     & Size ($\mu$m) \\
%     \midrule
%     Dendrite & Input terminal  & $\sim$100     \\
%     Axon     & Output terminal & $\sim$10      \\
%     Soma     & Cell body       & up to $106$  \\
%     \bottomrule
%   \end{tabular}
% \end{table}

>>>>

LLGP performed slightly worse than COGP in SMSE, but both NLPD and runtime indicate significant improvements (Tab.~\ref{weather-tbl}). Varying the number of interpolating points $m$ from $500$ to $1000$ constructs a tradeoff frontier between increases in $m$ and NLPD decrease at the cost of additional runtime (Fig.~\ref{fig:llgpweather}). While NLPD improvement diminishes as $m$ increases, LLGP is still an improvement compared to COGP for a range of $m$ by an order of magnitude in runtime and almost two orders of magnitude for NLPD.

@@

LLGP provides a means to approximate the log-likelihood function gradients through interpolation. We have shown on several datasets that this can be done in a way that is faster and leads to more accurate results than variational approximations. Because LLGP's representation can be efficient without being sparse (i.e., $m$ may be large), it can can capture complex interactions in the covariance. As pictured in Fig.~\ref{fx2007-graph}, and demonstrated by NLPD performance on both the FX2007 and weather datasets (Tab.~\ref{fx2007-tbl},\ref{weather-tbl}), such an efficient, non-sparse representation is integral to making a model whose confidence at a test site reflects the amount of related training data for that site.

@@
